### 2018-10-08 Sections/protocols_for_the_quantum_internet.tex
minor

An alternate approach is to use W-state encoding\index{W-state encoding} to implement unitary error averaging (Sec.~\ref{sec:error_averaging})\index{Unitary error averaging}, where the unitaries are single-qubit channels \cite{errorfilteringpaper, bib:MadhavPeterLund}. The protocol is shown in Fig.~\ref{fig:W_state_memory}. We begin by using a QFT fanout\index{Fanout} operation to encode a dual-rail encoded qubit\index{Dual-rail encoding} across $N$ optical modes. Each optical mode then feeds into a solid-state qubit (e.g a two-level atom), which ideally implement an identity channel but are inevitably subject to usual error processes such as dephasing and amplitude damping (characterised by $T_1$ and $T_2$ times). Finally, the inverse fanout operation is applied and success of the protocol is defined as there being exactly one photon between the first two (`success') output modes. If a photon is detected in any of the other (`failure') modes the state is presumed erroneous and discarded.

>>>>

An alternate approach is to use W-state encoding\index{W-state encoding} to implement unitary error averaging (Sec.~\ref{sec:error_averaging})\index{Unitary error averaging}, where the unitaries are single-qubit channels \cite{errorfilteringpaper, bib:MadhavPeterLund}. The protocol is shown in Fig.~\ref{fig:W_state_memory}. We begin by using a QFT fanout\index{Fanout} operation to encode a dual-rail encoded qubit\index{Dual-rail encoding} across $N$ optical modes. Each optical mode then feeds into a solid-state qubit (e.g a two-level atom), which ideally implement an identity channel but are inevitably subject to usual error processes such as dephasing and amplitude damping (characterised by $T_1$ and $T_2$ times\index{T$_2$-time}\index{T$_1$-time}). Finally, the inverse fanout operation is applied and success of the protocol is defined as there being exactly one photon between the first two (`success') output modes. If a photon is detected in any of the other (`failure') modes the state is presumed erroneous and discarded.
